Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2022-03-08 authors_responses/conditional_accept/authors_response.tex
Several more responses to reviewer 2 and 3 and accompanying changes to the paper

We are sorry for the confusion, the first use of the term ``Indistinguishability under the Chosen Plaintext Attack (IND-CPA)'' is in section II.A and has been referenced (reference [21]). The full cryptographic game which defines it was present in the appendix of the initial submission but removed due to initial reviews requesting fewer cryptographic background information. We hope this clears up why the definition is only referenced.

@@

@@

We're sorry this wan't clearer.

\dots quantisation noise is negligible when the quantised integer bit size is larger than the bit size of used floating-point numbers

@@

@@

@@

>>>>

We are sorry for the confusion, the first use of the term ``Indistinguishability under the Chosen Plaintext Attack (IND-CPA)'' is in section II.A and has been referenced (reference [21]). The full cryptographic game which defines it was present in the appendix of the initial submission but removed due to initial reviews requesting fewer cryptographic background information. For this reason, we have left the definition only referenced and hope this is found satisfactory.

@@

It is hard to say explicitly whether a filter udpate of $1.7s$ is compatible with real-time computation as this is dependent on the use-case (for example, infrequent measurements may suffice for the localisation of a slow-moving object such as a hot air baloon but would be insufficient for a fast moving object such as a jet). In addition, a further optimised implementation executed on more powerful hardware could result in significantly faster runtimes.

\textit{+changes made} time was used primarily as a comparitive measure in key sizes.

@@

We're sorry this wan't clearer. The quantisation noise is captured by the precision parameter $\phi$, which results in less noise when the parameter is large but is upper-bounded by $(20)$. Here, it is noted that when $M=N$, the upper bound can be practically ignored since $\phi$ can be chosen to have a bit-length much larger than a floating-point number, making any introduced encoding noise negligible. When pseudocode is presented in subsection V.C, $M=N$ is chosen, and in the results section VI, $\phi=2^{32}$ leads to a negligible difference in performance between an unencrypted (and unquantised) EIF and the presented quantised and encrypted one. We have udpated subsection V.C to make this clearer and hope that explains why there is no need for the quantisation noise to be considered in the filter.

@@

We apologise for having missed these, the full names have now been added.

@@

Thank you for noticing this. We have updated the notation section and other places throughout the text to remove the found errors.

@@

In practice, chosen cryptographic key size is dependent on the required length of secrecy and the planned lifetime of the used secret key. For example, if the location of an object needs only be private on the day of travel and new keys are generated each day, a shorter key can be used than for an object whose past location must not be leaked for the foreseeable future. Since cryptographic \textit{guarantees} are required, computation is not directly considered when choosing key sizes. However, in cases where computation makes desired cryptograhpic guarantees infeasible, shorter required secrecy or more frequent key exchanges can be considered to reduce key sizes and computation times.

\textit{+changes made}

### 2022-03-08 main.tex
Several more responses to reviewer 2 and 3 and accompanying changes to the paper

Typical cryptographic secrecy involves hiding all transferred data such that external parties in the communication network learn no new information from acquired encryptions. This can be achieved with common symmetric and public-key encryption scheme such as AES \cite{gueronIntelAdvancedEncryption2010} and RSA \cite{rivestMethodObtainingDigital1978}, respectively. In some cases however, partial data leakage or encrypted data processing is required for achieving a desired goal which has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in signal processing or localisation tasks. In \cite{alanwarPrOLocResilientLocalization2017}, homomorphic encryption is used to make time-independent model-free location estimates where an estimator cannot learn sensor measurements or locations. In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present. In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, centralised and hidden weighted sum aggregations, pWSAc and pWSAh, are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.

@@

\subsection{Notation}
Throughout this work, we make use of the following notation. Underlined characters, $\vec{a}$, denote vectors, uppercase bold characters, $\mat{A}$, denote matrices. $\mat{A}^{-1}$ is the matrix inverse while $\mat{A}^\top$ is its transpose. The expected value of a random variable is denoted $\mathsf{E}[\cdot]$, while the variance of a random scalar and covariance of a random vector by $\mathsf{Var}[\cdot]$ and $\mathsf{Cov}[\cdot]$, respectively. $|a|$ denotes absolute value, $\lVert\vec{a}\rVert$ the vector norm, $\{\dots\}$ is used for sets and $\langle\dots\rangle$ for ordered sequences. When estimating a state, notation $\hat{\vec{x}}_{k|l}$ will denote an estimate of $\vec{x}$ at timestep $k$ given measurements from timesteps up to and including $l$. When discussing cryptography, $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$ will denote encryption and decryption with key $k$, respectively, with $k$ ommited when inferrable from context. $\mathbb{Z}_n$ is used for the set of integers modulo $n$ and $\mathbb{Z}^*_n$ for its multiplicative group. $\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator and the term \textit{negligible function} refers to its cryptographic definition in \cite{katzIntroductionModernCryptography2008}.

@@

Encryption of a plaintext message $a \in \mathbb{Z}_N$, producing ciphertext $c \in \mathbb{Z}^{*}_{N^2}$, is computed by
\begin{equation}
    c = g^a \rho^N \pmod{N^2}
\end{equation}
for a randomly chosen $\rho \in \mathbb{Z}_{N}$. Here, $\rho^N$ can be considered the noise term which hides the value $g^a \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm. The decryption of a ciphertext is computed by
\begin{equation}
    a = \frac{L(c^\lambda\pmod{N^2})}{L(g^\lambda\pmod{N^2})} \pmod{N}
\end{equation}
where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$.

@@

We will consider a subset of rational numbers in terms of a range $M \in \mathbb{N}$ and fractional precision $\phi \in \mathbb{N}$. This contrasts with the common definition in terms of total and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not a power of two. A rational subset $\mathbb{Q}_{M,\phi}$ is then given by
\begin{equation}
    \mathbb{Q}_{M,\phi} = \left\{q \,\middle|\, \phi q \in \mathbb{N} \wedge -\left\lfloor\frac{M}{2}\right\rfloor \leq \phi q < \left\lfloor\frac{M}{2}\right\rfloor \right\}\,,
\end{equation}
and we can quantize any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$, that is, $\argmin_{q\in\mathbb{Q}_{M,\phi}} |a-q|$. In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to an encryption range $\mathbb{Z}_N$ is achieved by choosing $M=N$ and handling negatives by modulo arithmetic. Additionally, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication. This is captured by a third parameter $d$; the number of precision factors present in encodings.

@@

In general, the choice of a large precision parameter $\phi$ may reduce quantisation errors introduced in \eqref{eqn:encode}, but risks overflow after too many multiplications. Given the largest number of encoded multiplications, $d_{max}$, and the largest value to be encoded $a_{max}$, the parameter should be chosen such that
\begin{equation}
    \left|\phi^{d_{max}+1}a_{max}\right| < \left\lfloor \frac{M}{2} \right\rfloor\,.
\end{equation}
In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $M=N$.

@@

    \item[$\mathsf{AggDec}(t_{k,\tau}, pk_0, sk_0, l^{(k,\tau)}_1,\dots,l^{(k,\tau)}_n)$] Aggregation is computed as $l^{(k,\tau)} = \prod^n_{i=1}l^{(k,\tau)}_i \pmod{N^2}$, removing the aggregation noise terms, and is followed by Paillier scheme decryption
    \begin{equation}
        \begin{split}
            \sum^{n}_{i=1}\sum^{m}_{j=1}&a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j =\\
            &\frac{L((l^{(k,\tau)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,,
        \end{split} \label{eqn:our_scheme_decrypt}
    \end{equation}
    with $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$. The correctness of the aggregation can be seen from
    \begin{align*}
        \begin{split}
        l^{(k,\tau)} &= \prod^n_{i=1}H(t_{k,\tau})^{sk_i}\cdot \\
        &\qquad (N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \!\!\pmod{N^2}
        \end{split}\\
        \begin{split}
            &= H(t_{k,\tau})^{\sum^n_{i=1}sk_i}\cdot \\
            &\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \!\!\pmod{N^2}
        \end{split}\\
        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho'^N \!\!\pmod{N^2}\,,
    \end{align*}
    for some values $\rho_i,\rho' \in \mathbb{Z}_N,\,i\in\{1,\dots,n\}$.
\end{LaTeXdescription}
Additionally, we note that in the above construction, all weights $\omega^{(k,\tau)}_j$ and values $a^{(k,\tau)}_{i,j}$ are integers and the resulting linear combinations and aggregation are computed modulo $N$.

>>>>

Typical cryptographic secrecy involves hiding all transferred data such that external parties in the communication network learn no new information from acquired encryptions. This can be achieved with common symmetric and public-key encryption schemes such as the Advanced Encryption Standard (AES) \cite{gueronIntelAdvancedEncryption2010} and the Rivest-Shamir-Adleman cryptosystem (RSA) \cite{rivestMethodObtainingDigital1978}, respectively. In some cases however, partial data leakage or encrypted data processing is required for achieving a desired goal which has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in signal processing or localisation tasks. In \cite{alanwarPrOLocResilientLocalization2017}, homomorphic encryption is used to make time-independent model-free location estimates where an estimator cannot learn sensor measurements or locations. In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present. In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, private Weighted Sum Aggregation with centralised and hidden weights (pWSAc and pWSAh, respectively) are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.

@@

\subsection{Notation}
Throughout this work, we make use of the following notation. Underlined characters, $\vec{a}$, denote vectors, uppercase bold characters, $\mat{A}$, denote matrices. $\mat{A}^{-1}$ is the matrix inverse while $\mat{A}^\top$ is its transpose. The expected value of a random variable is denoted $\mathsf{E}[\cdot]$, while the variance of a random scalar and covariance of a random vector by $\mathsf{Var}[\cdot]$ and $\mathsf{Cov}[\cdot]$, respectively. $|a|$ denotes absolute value, $\lVert\vec{a}\rVert$ the vector norm, $\{\dots\}$ is used for sets and $\langle\dots\rangle$ for ordered sequences. When estimating a state, notation $\hat{\vec{x}}_{k|e}$ will denote an estimate of $\vec{x}$ at timestep $k$ given measurements from timesteps up to and including timestep $e$. When discussing cryptography, $\mathcal{E}_{sk}(\cdot)$ and $\mathcal{D}_{sk}(\cdot)$ will denote encryption and decryption with key $sk$, respectively, with $sk$ ommited when inferrable from context. $\mathbb{Z}_N$ is used for the set of integers modulo $N$ and $\mathbb{Z}^*_N$ for its multiplicative group. $\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator and the term \textit{negligible function} refers to its cryptographic definition in \cite{katzIntroductionModernCryptography2008}.

@@

Encryption of a plaintext message $a \in \mathbb{Z}_N$, producing ciphertext $c \in \mathbb{Z}^{*}_{N^2}$, is computed by
\begin{equation}
    c = g^a \rho^N \pmod{N^2}
\end{equation}
for a randomly chosen $\rho \in \mathbb{Z}_{N}$. Here, $\rho^N$ can be considered the noise term which hides the value $g^a \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm. The decryption of a ciphertext is computed by
\begin{equation}
    a = \frac{L(c^\lambda\pmod{N^2})}{L(g^\lambda\pmod{N^2})} \pmod{N}
\end{equation}
where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(\psi) = \frac{\psi-1}{N}$.

@@

We will consider a subset of rational numbers in terms of a range $M \in \mathbb{N}$ and fractional precision $\phi \in \mathbb{N}$. This contrasts with the common definition in terms of total and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not a power of two. A rational subset $\mathbb{Q}_{M,\phi}$ is then given by
\begin{equation}
    \mathbb{Q}_{M,\phi} = \left\{o \,\middle|\, \phi o \in \mathbb{N} \wedge -\left\lfloor\frac{M}{2}\right\rfloor \leq \phi o < \left\lfloor\frac{M}{2}\right\rfloor \right\}\,,
\end{equation}
and we can quantize any real number $a$ by taking the nearest rational $o \in \mathbb{Q}_{M,\phi}$, that is, $\argmin_{o\in\mathbb{Q}_{M,\phi}} |a-o|$. In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to an encryption range $\mathbb{Z}_N$ is achieved by choosing $M=N$ and handling negatives by modulo arithmetic. Additionally, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication. This is captured by a third parameter $d$; the number of additional precision factors present in encodings.

@@

In general, the choice of a large precision parameter $\phi$ may reduce quantisation errors introduced in \eqref{eqn:encode}, but risks overflow after too many multiplications. Given the largest number of encoded multiplications, $d_{max}$, and the largest value to be encoded $a_{max}$, the parameter should be chosen such that
\begin{equation}
    \left|\phi^{d_{max}+1}a_{max}\right| < \left\lfloor \frac{M}{2} \right\rfloor\,.
\end{equation}
In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $M=N$, as $\phi$ can be made sufficiently large to make quantisation errors negligible.

@@

    \item[$\mathsf{AggDec}(t_{k,\tau}, pk_0, sk_0, l^{(k,\tau)}_1,\dots,l^{(k,\tau)}_n)$] Aggregation is computed as $l^{(k,\tau)} = \prod^n_{i=1}l^{(k,\tau)}_i \pmod{N^2}$, removing the aggregation noise terms, and is followed by Paillier scheme decryption
    \begin{equation}
        \begin{split}
            \sum^{n}_{i=1}\sum^{m}_{j=1}&a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j =\\
            &\frac{L((l^{(k,\tau)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,,
        \end{split} \label{eqn:our_scheme_decrypt}
    \end{equation}
    with $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(\psi) = \frac{\psi-1}{N}$. The correctness of the aggregation can be seen from
    \begin{align*}
        \begin{split}
        l^{(k,\tau)} &= \prod^n_{i=1}H(t_{k,\tau})^{sk_i}\cdot \\
        &\qquad (N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \!\!\pmod{N^2}
        \end{split}\\
        \begin{split}
            &= H(t_{k,\tau})^{\sum^n_{i=1}sk_i}\cdot \\
            &\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \!\!\pmod{N^2}
        \end{split}\\
        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho'^N \!\!\pmod{N^2}\,,
    \end{align*}
    for some values $\rho_i,\rho' \in \mathbb{Z}_N,\,i\in\{1,\dots,n\}$.
\end{LaTeXdescription}
Additionally, we note that in the above construction, all weights $\omega^{(k,\tau)}_j$ and values $a^{(k,\tau)}_{i,j}$ are integers and the resulting linear combinations and aggregation are computed modulo $N$.
